\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-24 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added appendix with proof sf that SGS=S

	\section{Appendix}
	%\thisfloatpagestyle{empty}
	\input{Appendix}

	\newpage

>>>>

	\section{Appendix}
	%\thisfloatpagestyle{empty}
	\subsection{Proof $\bm{S}\bm{G}\bm{S}=\bm{S}$ implies $\bm{S}\bm{G}$ is a projection}
	Here we establish that if $\bm{S}\bm{G}$ is a projection onto the linear subspace spanned by $\bm{S}$ then $\bm{S}\bm{G}\bm{S}=\bm{S}$.  We also prove that the converse holds, namely that if the condition $\bm{S}\bm{G}\bm{S}=\bm{S}$ holds then $\bm{S}\bm{G}$ must be a projection onto the linear subspace spanned by $\bm{S}$.

	To establish the first statement let $\bm{s}_j$ be the $j^{th}$ column of $\bm{S}$.  Since by definition, $\bm{s}_j$ lies in in $\mathfrak{s}$, it must hold that $\bm{S}\bm{G}\bm{s}_j=\bm{s}_j$.  Stacking these vectors horizontally
	\begin{align}
	\bm{S}\bm{G}\bm{S}&=\begin{pmatrix}
	\bm{S}\bm{G}\bm{s}_1, & \bm{S}\bm{G}\bm{s}_2, & \cdots & \bm{S}\bm{G}\bm{s}_m
	\end{pmatrix}\\
	&=\begin{pmatrix}
	\bm{s}_1, & \bm{s}_2, & \cdots & \bm{s}_m
	\end{pmatrix}\\
	&=\bm{S}
	\end{align}

	To establish the converse it suffices to postmultiply the condition $\bm{S}\bm{G}\bm{S}=\bm{S}$ by $\bm{G}$.  This yields $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ which in turn implies idempotence since $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$.
	\input{Appendix}
	\newpage
